---
title: "Loading WoS data"
author: "Kristine"
date: "27/4/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
pacman::p_load(tidyverse,
               dplyr,
               plyr,
               stringr,
               readxl,
               purrr,
               genderizeR)

```

Loading all data
```{r}
#listing files
data.list <- list.files(pattern = '*.xls')

#read files 
dat = lapply(data.list, function(i){
    x = read_excel(i)
    
    x
})

#making dataframe 
df <- ldply (dat, data.frame)

#save csv
write_csv(df, "alldata.csv") 
```


Cleaning data
We need to find:
- first authors first name (Author.Full.Names)
- last authors first name
- papers where first author is from Aarhus university
```{r}
#read csv with all files
#df <- read.csv("alldata.csv")



#Making empty columns to fill
dfnames <- df %>% 
    mutate(
      First.Author.Name = Author.Full.Names,
      Last.Author.Name = Author.Full.Names)

#extracting first and last author names - full names 
dfnames <- dfnames %>%
  mutate(
    First.Author.Name = gsub(";.*", '', First.Author.Name),
    Last.Author.Name = gsub(".*;", '', Last.Author.Name)
  )

#Finding first name only
# - first name is after comma
dfnames <- dfnames %>%
  mutate(
    First.Author.Name = gsub(".*,", '', First.Author.Name),
    Last.Author.Name = gsub(".*,", '', Last.Author.Name)
  )

#removing space in front of first character
dfnames <- dfnames %>%
  mutate(
    First.Author.Name = str_replace(First.Author.Name, " ", ""),
    Last.Author.Name = str_replace(Last.Author.Name, " ", "")
  )

# - only keep one name if several is listed (first name before space)
dfnames <- dfnames %>%
  mutate(
    First.Author.Name = gsub(" .*", '', First.Author.Name),
    Last.Author.Name = gsub(" .*", '', Last.Author.Name)
  )


```


Finding papers with first author from Aarhus university
```{r}
#extract characters after ] in Addresses
aarhuspapers <- dfnames %>%
  mutate(
    First.Author.University = gsub(".*]", '', Addresses)
  )

#remove space in front of characters   
aarhuspapers <- aarhuspapers %>%
  mutate(
    First.Author.University = str_replace(First.Author.University, " ", "")
  ) 

#Extract characters before comma
aarhuspapers <- aarhuspapers %>%
  mutate(
    First.Author.University = gsub(",.*", '', First.Author.University)
  )

#we have a total of 29154 observations from all universities

#Now we only find papers from Aarhus university

#aarhuspapersfactor <- aarhuspapers %>%
#  mutate(
#    First.Author.University = as.factor(First.Author.University)
#  )
#aarhuspapersfactor$First.Author.University

#factor = 5098 universities
#We have a total of 5098 different firt author universities in the full dataset

#filtering only Aarhus univeristy
aarhuspapers <- aarhuspapers %>%
  dplyr::filter(First.Author.University == "Aarhus Univ")

#9318 observations, papers form Aarhus uni 
#note some papers might have used another wording for Aarhus university e.g University Aarhus - these are not included as I only eyeballed 3 or something
# Could also consider if we should include papers from Aarhus university hospital
```


Variables to keep:
- Article title
- First author name
- Last author name
- Abstract
- Citations (find den rigtige)
- publication year
- Research area (tror det er det tætteste we kommer på fakultet)

```{r}
#selecting only interesting variables
newdf <- aarhuspapers %>%
  subset(
    select = c("Article.Title",
               "Abstract",
               "Cited.Reference.Count",
               "Times.Cited..WoS.Core",
               "Times.Cited..All.Databases",
               "Since.2013.Usage.Count",
               "Publisher",
               "Publication.Year",
               "WoS.Categories",
               "Research.Areas",
               "First.Author.Name",
               "Last.Author.Name",
               "First.Author.University")
  )

write.csv(newdf, "cleandata.csv")

```

Define gender of first author and second author
- using genderizeR
- adding two new columns

```{r}

#newdf <- read.csv("cleandata.csv")

#Predicting first author gender using API-key
First.Author.Gender <- findGivenNames(newdf$First.Author.Name, textPrepare = FALSE, country = NULL, language = NULL, apikey = "eabaf20628864c8dff0f446d606570a9", queryLength = 10,progress = FALSE, ssl.verifypeer = FALSE)

#Predicting last author gender using API-key
Last.Authour.Gender <- findGivenNames(newdf$Last.Author.Name, textPrepare = FALSE, country = NULL, language = NULL, apikey = "eabaf20628864c8dff0f446d606570a9", queryLength = 10, progress = FALSE, ssl.verifypeer = FALSE)


#firstname_gender <- First.Author.Gender #%>% 
#  mutate(
#    name = as.character(name),
#    gender = as.character(gender),
#    probability = #as.numeric(probability),
#    count = as.numeric(count),
#    country_id = as.character(country_id)
#  )

#Renaming variables first author
First.Author.Gender <- First.Author.Gender %>% 
  dplyr::rename(
    First.Author.Name = name,
    First.Author.Gender = gender,
    First.Author.Gender.Probability = probability,
    First.Author.Gender.Count = count,
    First.Author.Gender.Country_ID = country_id
  )

#Renaming variables last author
Last.Authour.Gender <- Last.Authour.Gender %>% 
  dplyr::rename(
    Last.Author.Name = name,
    Last.Author.Gender = gender,
    Last.Author.Gender.Probability = probability,
    Last.Author.Gender.Count = count,
    Last.Author.Gender.Country_ID = country_id
  )


#merging df with gender dataframe by Author.First.Name
firstnew <- merge(newdf,First.Author.Gender, by = "First.Author.Name")

#Removing dublicates
firstnew <- firstnew %>% distinct(Article.Title,.keep_all = TRUE)


#Merging df with last Author gender
semifinaldf <- merge(firstnew,Last.Authour.Gender, by = "Last.Author.Name")

#Removing dublicates
semifinaldf <- semifinaldf %>% distinct(Article.Title,.keep_all = TRUE)


#save csv 
write.csv(semifinaldf, "semifinaldf.csv")
```

Removing Abstracts with NA
```{r}
semifinaldf <- semifinaldf %>% filter(!is.na(Abstract))
```


Exploring research areas
```{r}

semifinaldf <- read.csv("semifinaldf.csv")


semifinaldf <- semifinaldf %>%
  mutate(
    WoS.Categories = as.factor(WoS.Categories),
    Research.Areas = as.factor(Research.Areas),
    First.Author.Gender = as.factor(First.Author.Gender),
    Last.Author.Gender = as.factor(Last.Author.Gender)
  )

#finding only first mentioned research area

semifinaldf <- semifinaldf %>%
  mutate(
    Research.Areas = gsub(";.*", '', Research.Areas)
  )

semifinaldf <- semifinaldf %>%
  mutate(
    Research.Areas = gsub(",.*", '', Research.Areas)
  )

semifinaldf <- semifinaldf %>%
  mutate(
    Research.Areas = gsub("&.*", '', Research.Areas)
  )



write.csv(semifinaldf, "semifinaldf.csv")


```

```{r}
#Loading the "clean" data with NA removed and summarized areas of research 

df <- read_csv("semifinaldf.csv")

#Removing extra (X) columns from download 
#df <- df[, -c(1:2)] #delete column 5


#How many research areas do we have
df$Research.Areas <- as.factor(df$Research.Areas)
levels(df$Research.Areas)

#We still have 142 different categories, which would we like to seperate into Faculties equivalent to Aarhus university. 

Area_df <- df %>% select(Research.Areas )

Area_df <- unique(Area_df, incomparables = FALSE)
Area_df <- Area_df %>% filter(!is.na(Research.Areas))

write_csv(Area_df, "Area_of_research.csv") 

df2 <- read_delim("Area_of_research_2.csv", delim = ";", col_names = TRUE,col_types = NULL)

#The df2 now contains a specification of which faculty each Area of Research has.

#No idea why the renaming does not work 
names(df2)[names(df2) == "`Faculty `"] <- "Faculty"
names(df2)[names(df2) == "`Area `"] <- "Area"

#the plot shows how reserach areas are seperated into faculties       
ggplot(df2, aes(`Faculty `, fill= `Faculty `))+ geom_bar()
```


```{r}
#Further data cleaning to assign faculty to each research area 

###MESSY DATA CLEANING TO ASSIGN EACH RESEARCH AREA TO A FACULTY. 
##Dont run this again - just load the df_w_faculty.csv - it has been cleaned 


#Create a new column in df where faculty should be listed - I created df test to ensure im not messing with our so far clean data 

df_test <- df 

df_test <- mutate(df_test, Faculty = ifelse(Research.Areas== "Religion" 
                                            |Research.Areas == "Anthropology"|Research.Areas == "Area Studies" 
                                            |Research.Areas == "Public Administarion"
                                            |Research.Areas == "Cultural studies" 
                                            |Research.Areas == "Communication"
                                            |Research.Areas == "Philosophy"
                                            |Research.Areas == "Education"
                                            |Research.Areas == "Linguistics" 
                                            |Research.Areas == "Social Sciences - Other Topics"
                                            |Research.Areas == "History"
                                            |Research.Areas == "Mathematical Methods In Social Sciences"
                                            |Research.Areas == "Art" 
                                            |Research.Areas == "Film"
                                            |Research.Areas == "Ethnic studies"
                                            |Research.Areas == "Instruments" 
                                            |Research.Areas == "Music"
                                            |Research.Areas == "Literature"
                                            |Research.Areas == "Theater" 
                                            |Research.Areas == "Socail Issues"
                                            |Research.Areas == "Sociology"
                                            |Research.Areas == "History" 
                                            |Research.Areas == "Archaeology"
                                            |Research.Areas == "Information Sciences"
                                            |Research.Areas == "Arts" 
                                            |Research.Areas == "Classics"
                                            |Research.Areas == "Women's Studies"
                                            |Research.Areas == "Asian Studies", 'a', ""))


df_test <- mutate(df_test, Faculty = ifelse(Research.Areas== "Business"
                          |Research.Areas == "Government"
                          |Research.Areas == "Behavioral Sciences" 
                                            |Research.Areas == "Materials Science"
                                            |Research.Areas == "Psychology"
                                            |Research.Areas == "Public" 
                                            |Research.Areas == "Demography"
                                            |Research.Areas == "Criminology"
                                            |Research.Areas == "Development Studies"
                                            |Research.Areas == "Substance Abuse"
                                            |Research.Areas == "Family Studies"
                                            |Research.Areas == "Social Work"
                                            |Research.Areas == "Urban Studies", 'b', Faculty))


df_test <- mutate(df_test, Faculty = ifelse(Research.Areas== "Chemistry"
                                            |Research.Areas == "Elctrochemistry"
                                            |Research.Areas == "Geology" 
                                            |Research.Areas == "Plant Sciences"
                                            |Research.Areas == "Genetics"
                                            |Research.Areas == "Science" 
                                            |Research.Areas == "Microbiology"
                                            |Research.Areas == "Physics"
                                            |Research.Areas == "Research"
                                            |Research.Areas == "Polymer Science"
                                            |Research.Areas == "Astronomy"
                                            |Research.Areas == "Physical Geography"
                                            |Research.Areas == "Computer Science" 
                                            |Research.Areas == "Marine"
                                            |Research.Areas == "Biodiversity" 
                                            |Research.Areas == "Construction"
                                            |Research.Areas == "Meteorology"
                                            |Research.Areas == "Energy"
                                            |Research.Areas == "Mathematics"
                                            |Research.Areas == "Biotechnology"
                                            |Research.Areas == "Physical Geography"
                                            |Research.Areas == "Mycology"
                                            |Research.Areas == "Geography"
                                            |Research.Areas == "Cell Biology"
                                            |Research.Areas == "Oceanography" 
                                            |Research.Areas == "Evolutionary Biology"
                                            |Research.Areas == "Thermodynamics"
                                            |Research.Areas == "Mathematical"
                                            |Research.Areas == "Nuclear Science"
                                            |Research.Areas == "Developmental Biology"
                                            |Research.Areas == "Reproductive Biology"
                                            |Research.Areas == "Imaging Science"
                                            |Research.Areas == "Crystalllography",
                                            'n', Faculty))


df_test <- mutate(df_test, Faculty = ifelse(Research.Areas== "Biohemistry"
                                            |Research.Areas == "Forestry"	
                                            |Research.Areas == "Telecommunications" 
                                            |Research.Areas == "Agriculture"
                                            |Research.Areas == "Environmental Sciences"
                                            |Research.Areas == "Engineering"			
                                            |Research.Areas == "Life Sciences"
                                            |Research.Areas == "Geochemistry"
                                            |Research.Areas == "Zoology"
                                            |Research.Areas == "Veterinary Sciences"
                                            |Research.Areas == "Entomology"
                                            |Research.Areas == "Nutrition"
                                            |Research.Areas == "Mechanics" 
                                            |Research.Areas == "Food Science"
                                            |Research.Areas == "Automation" 
                                            |Research.Areas == "Fisheries"
                                            |Research.Areas == "Biophysics"
                                            |Research.Areas == "Remote Sensing"
                                            |Research.Areas == "Acoustics"
                                            |Research.Areas == "Robotics"
                                            |Research.Areas == "Water Resources"
                                            |Research.Areas == "Architecture",
                                            't', Faculty))

#Adding the faculty h (health) on all the Articles that haven't been assigned another faculty. 
df_test <- mutate(df_test, Faculty = ifelse(Faculty == "",
                                            'h', Faculty))



#Write csv so we don't have to run this mess again

write_csv(df_test, "df_w_faculty.csv") 

```


```{r}
#Replacing Author Names that were not gender indentified with a probability above 0.7 with NA 

#Do we have the gender of all Authors - and how sure was Genderize 

df <- read_csv("df_w_faculty.csv") 
ggplot(df, aes(x = as.numeric(First.Author.Gender.Probability)))+
  geom_histogram(aes(y=..density..))

ggplot(df_gender_last, aes(x = as.numeric(Last.Author.Gender.Probability)))+
  geom_histogram(aes(y=..density..))

#QUOESTION- should we remove the papers where genderize isn't super sure? 
#Remember that just because it is unsure about first author gender then it isn't unsure about last author, so a lot of data we are possibly throwing away. It also has a hard time on Asian names. And i can see that it classifies Andrea as male, Janne as male and Kim as female just as an example. 


#Finding the cases where both first and last author have below 0.70 probability for correct gender identification

df_gender <- df %>%  filter(First.Author.Gender.Probability < 0.70 & Last.Author.Gender.Probability < 0.70)

#removing them from our data 

df <- df %>% filter(!(First.Author.Gender.Probability < 0.70 & Last.Author.Gender.Probability < 0.70))

#Finding how many cases where either first or last author gender probability is below 0.70

df_gender_last <- df %>% filter(Last.Author.Gender.Probability < 0.70)

df_gender_last <- df_gender_last %>% select(c(Last.Author.Name, Last.Author.Gender.Probability,Last.Author.Gender))

df_gender_first <- df %>% filter(First.Author.Gender.Probability < 0.70)


df_gender_first <- df_gender_first %>% select(c(First.Author.Name, First.Author.Gender.Probability,First.Author.Gender))



#Replacing genders with low probability with NA 

df<- df %>% mutate(First.Author.Gender = ifelse(First.Author.Gender.Probability < 0.70, NA, First.Author.Gender))
df<- df %>% mutate(Last.Author.Gender = ifelse(Last.Author.Gender.Probability < 0.70, NA, Last.Author.Gender))



```

Abstract lengths of characters
```{r}
library(stringr)
library(dplyr)

#Counting words in each abstract
df <- df %>% 
  mutate(wordcount = str_count(df$Abstract, pattern = "\\w+"))

#we have abstracts with 8 words and 922/939 words 
range(df$wordcount)

#The histogram shows the distribution of abstract lengths - shows that it makes sense to have a max length of 500 for our BERT as the tail is very long
ggplot(df, aes(x = as.numeric(wordcount)))+
  geom_histogram(aes(y=..density..))
#Super thin tail on our distribution - so we remove articles with more than 500 words. 

df <- df %>% filter(wordcount< 500)

#How many papers do we have?
# We have 8134 Articles 

length(df$Article.Title) 

```

writing csv ready for sentiment analysis
```{r}
write_csv(df, "df_ready_BERT.csv") 
```

