---
title: "Exploring"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
#Loading packages 
pacman::p_load(tidyverse,
               dplyr,
               plyr,
               stringr,
               readxl,
               purrr,
               koRpus,
               readxl)

```


```{r}
#load data 

df <- read_csv("df_lix_sentiment_confidence.csv")

```

Removing NA's from Gender
```{r}
df <- df %>%
  drop_na(First.Gender)

df <- df %>%
  drop_na(Last.Gender)

df <- df %>%
  drop_na(Faculty)
```


```{r}
#Exploring our data 

#How is the gender distribution in general (first author)?

ggplot(df, aes(First.Author.Gender, fill = First.Author.Gender)) + geom_bar()

#How is the gender distribution in general (last author)?
#Comment for the plot. it is interesting to see that there is a lot more male last authors, indicating that many of the head of departments are male. There is an increase in male last authors compared to male first authors and the female authors is in outnumbered in both conditions. 

ggplot(df, aes(Last.Author.Gender, fill = Last.Author.Gender)) + geom_bar()

#How is the gender distribution in years (first author)?
#these plots would be more informative if the bars were placed next to eachother, but I dont know how to do that, without specifying a y-axis. 

ggplot(df, aes(Publication.Year, fill = First.Author.Gender)) + geom_bar()


#How is the gender distribution in years (last author)?

ggplot(df, aes(x = Publication.Year, fill = Last.Author.Gender)) + 
  geom_bar()
  
  
#Abstract sentences 
#We are moving into the realm of NLP maybe we should leave that for Python :-) 

##Faculties  

ggplot(df, aes(x = Faculty, fill = Faculty)) + 
  geom_bar()



```



```{r}

#Exploring gender distribution 
dfff <- df %>% filter(First.Author.Gender == "female")
dflf <- df %>% filter(Last.Author.Gender == "female")
dffm <- df %>% filter(First.Author.Gender == "male")
dflm <- df %>% filter(Last.Author.Gender == "male")


#Gender plots
ggplot(df, aes(First.Author.Gender, fill = First.Author.Gender)) + geom_bar()
ggplot(df, aes(Last.Author.Gender, fill = Last.Author.Gender)) + geom_bar()

#How is the gender distribution in years (first author)?

ggplot(df, aes(x= Publication.Year, fill = First.Author.Gender)) + geom_bar(position=position_dodge(preserve = "single"))

ggplot(df, aes(x= Publication.Year, fill = Last.Author.Gender)) + geom_bar(position=position_dodge(preserve = "single"))

```


Cutting papers with more than 150citations for plotting
```{r}
df_cit150 <- df %>%
  filter(Citations < 150)
```


```{r}
#Citations and first gender
ggplot(df_cit150, aes(Citations, fill =First.Gender)) + geom_density() + facet_wrap(~First.Gender)

#Citations and last gender
ggplot(df_cit150, aes(Citations, fill =Last.Gender)) + geom_density() + facet_wrap(~Last.Gender)

#Citations and Sentiment
ggplot(df_cit150, aes(Citations, fill =Sentiment)) + geom_density() + facet_wrap(~Sentiment)

#Citationes and sentiment in color
ggplot(df_cit150, aes(Citations, fill = Sentiment, color =Sentiment)) + geom_density( alpha=0.1) + facet_wrap(~First.Gender)
```


```{r}
#first author sentiment 
ggplot(df, aes(Sentiment, Citations, fill = First.Gender)) + geom_bar(position="dodge",  stat='summary', fun.y=mean) + geom_errorbar(stat='summary', fun.data=mean_se, width=0.2,position=position_dodge(0.9))

#Last author sentiment
ggplot(df, aes(Sentiment.label, fill = Last.Author.Gender)) + geom_bar(position=position_dodge(preserve = "single"))

#first author sentiment by faculty
ggplot(df, aes(Sentiment, Citations, fill = First.Gender)) + geom_bar(position="dodge",  stat='summary', fun.y=mean) + geom_errorbar(stat='summary', fun.data=mean_se, width=0.2,position=position_dodge(0.9)) + facet_wrap(~Faculty)

#Last author sentiment by faculty
ggplot(df, aes(Sentiment.label, fill = Last.Author.Gender)) + geom_bar(position=position_dodge(preserve = "single")) + facet_wrap(~Faculty)

```



```{r}
#First author - confidence 
ggplot(df, aes(First.Author.Gender, totalconfidence, fill = First.Author.Gender)) + geom_bar(position=position_dodge(preserve = "single"), stat='summary', fun.y=mean) + geom_errorbar(stat='summary', fun.data=mean_se, width=0.5)

#Faculty - confidence
ggplot(df, aes(Faculty, totalconfidence, fill = Faculty)) + geom_bar(position=position_dodge(preserve = "single"), stat='summary', fun.y=mean) + geom_errorbar(stat='summary', fun.data=mean_se, width=0.5) + facet_wrap(~First.Author.Gender)

#Last author - confidence
ggplot(df, aes(Last.Author.Gender, totalconfidence, fill = Last.Author.Gender)) + geom_bar(position=position_dodge(preserve = "single"), stat='summary', fun.y=mean) + geom_errorbar(stat='summary', fun.data=mean_se, width=0.5)


```


```{r}
#Citations for first gender in each faculty

ggplot(df, aes(Confidence, Citations, fill = First.Gender)) + geom_smooth(method = "lm") + facet_wrap(~Faculty)

```




```{r}
#year and first author
ggplot(df, aes(Publication.Year, fill = First.Author.Gender)) + geom_bar(position=position_dodge(preserve = "single"))

#Sentiment and first author
ggplot(df, aes(Sentiment.label, fill = First.Author.Gender)) + geom_bar(position=position_dodge(preserve = "single")) + facet_wrap(~Publication.Year)

```


```{r}
#plot showing mean citation count per year 
ggplot(df, aes(Publication.Year, Times.Cited..All.Databases, fill= Publication.Year))+
  geom_bar(stat = "summary", fun.y = mean) +
  stat_summary(aes(label=round(..y..,2)), fun.y=mean, geom="text", size=4, vjust = -0.3)
```

```{r}
With the clean dataframe and final models

dfplot <- read.csv("df_lix_sentiment_confidence.csv")

dfplot <- dfplot %>%
  mutate(
    Title = as.factor(Article.Title),
    Last.Gender = as.factor(Last.Author.Gender),
    First.Gender = as.factor(First.Author.Gender),
    Sentiment = as.factor(label),
    Faculty = as.factor(Faculty),
    Citations = as.numeric(Times.Cited..All.Databases),
    Year = as.numeric(Publication.Year),
    Confidence = as.numeric(totalconfidence)
    
  )


dfplot <- dfplot %>%
  select(
    Title,
    Last.Gender,
    First.Gender,
    Sentiment,
    Faculty,
    Citations,
    Year,
    Confidence
  )


```


Removing NA's from Gender
```{r}
df <- df %>%
  drop_na(First.Gender)

df <- df %>%
  drop_na(Last.Gender)

```


```{r}
#making new varaible with first and last gender collapsed 
dfplot <- dfplot %>%
  mutate(
    BothGender = paste0(First.Gender, Last.Gender))

dfplot <- dfplot %>%
  mutate(
    BothGender = as.factor(BothGender))

```

Renaming variables
```{r}
#renaming variables
dfplot <- dfplot %>%
  mutate(
    First.Author.Gender = First.Gender,
    Order.of.Gender = BothGender
    
  )

#renaming levels
dfplot <- dfplot %>%
  mutate(
    First.Author.Gender = revalue(First.Author.Gender, c("female"="First author female", "male"="First author male")))


```



Sentiment plot
```{r}
ggplot(dfplot, aes(x = Sentiment, y = Citations, fill = First.Gender)) + 
  geom_bar(position="dodge", stat='summary', fun.y=mean) +  geom_errorbar(stat='summary', 
                fun.data=mean_se, width=0.2, position=position_dodge(0.9))


ggplot(dfplot, aes(x = Sentiment, y = Citations, fill = Last.Gender)) + 
  geom_bar(position="dodge", stat='summary', fun.y=mean) +  geom_errorbar(stat='summary', 
                fun.data=mean_se, width=0.2, position=position_dodge(0.9))


ggplot(dfplot, aes(x = Sentiment, y = Citations, fill = Order.of.Gender)) + 
  geom_bar(position="dodge", stat='summary', fun.y=mean) +  geom_errorbar(stat='summary', 
                fun.data=mean_se, width=0.2, position=position_dodge(0.9)) + facet_wrap( ~ First.Author.Gender) + scale_fill_brewer(palette="PuOr") + theme_classic()


```



Confidence plot
```{r}
ggplot(df, aes(Confidence, Citations , color = First.Gender)) + geom_smooth(method = "lm") + facet_wrap(~ Faculty)
ggplot(df, aes(Confidence, Citations , color = Last.Gender)) + geom_smooth(method = "lm") + facet_wrap(~ Faculty)


#adding both first and last author, but coloring does not work. With it be nice to make a variable showing first+last gender in same
ggplot(df) + 
  geom_smooth(aes(Confidence, Citations, color = First.Gender), method = "lm", alpha = 0) +
  scale_color_manual(values=c("female" = "green",
                             "male" = "cyan",
                             "NA" = "black"),
                    name = "first author") +
  geom_smooth(aes(Confidence, Citations, color = Last.Gender), method = "lm", alpha = 0) +
  scale_color_manual(values=c("female" = "red",
                             "male" = "blue",
                             "NA" = "black"),
                      name = "last author")


#nice nok plot
ggplot(dfplot) + 
  geom_smooth(aes(Confidence, Citations, color = Order.of.Gender), method = "lm", alpha = 0.1) + facet_wrap(~First.Author.Gender) + scale_color_brewer(palette="PuOr") + theme_classic()
#First female and last female get a waaaay higher slope than first female and last male, however last male have a higher intercept
#Firsr male and last male have a positive interaction when increasing centiment, however this is opposite for male first, female last

```




Making estimates from model 1 - sentiment - called m1_post in analysis.Rmd
```{r}
mydatabsent <- dfplot

mydatabsent <- cbind(mydatabsent, fitted(m1_post, mydatabsent, re_formula=NA))

mydatabsent <- mydatabsent %>%
  drop_na(Estimate)

mydatabsent <- mydatabsent %>%
  mutate(
    Estimate.rneg = mean(rnegbin(1.e4, mu = exp(Estimate), theta = 0.57))
  )
```

Plotting estimates
```{r}
ggplot(mydatabsent, aes(x = Sentiment, y = Estimate, fill = Order.of.Gender)) + 
  geom_bar(position="dodge", stat='summary', fun.y=mean) +  geom_errorbar(stat='summary', 
                fun.data=mean_se, width=0.2, position=position_dodge(0.9)) + facet_wrap( ~ First.Author.Gender) + scale_fill_brewer(palette="PuOr") + theme_classic()

```


Making estimates from model 2 - confidence - called m2_post in analysis.Rmd
```{r}
mydatabcon <- dfplot

mydatabcon <- cbind(mydatabcon, fitted(m2_post, mydatabcon, re_formula=NA))

mydatabcon <- mydatabcon %>%
  drop_na(Estimate)

```


Plotting estimates
```{r}
ggplot(mydatabcon) + 
  geom_smooth(aes(Confidence, Estimate, color = Order.of.Gender, ymin = Q2.5, ymax = Q97.5, stat = "identity"), method = "lm", alpha = 0.1) + facet_wrap(~First.Author.Gender) + scale_color_brewer(palette="PuOr") + theme_classic()
```


Looking at year and it predicted estimates
```{r}
ggplot(dfplot, aes(x = Year, y = Citations)) + geom_smooth(method = "lm") + scale_color_brewer(palette="PuOr") + theme_classic()

ggplot(mydatabsent, aes(x = Year, y = Estimate)) + geom_smooth(method = "lm") + scale_color_brewer(palette="PuOr") + theme_classic()

ggplot(mydatabcon, aes(x = Year, y = Estimate)) + geom_smooth(method = "lm") + scale_color_brewer(palette="PuOr") + theme_classic()

```


